Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets

### 2021-11-03 manuscript/Manuscript.Rmd

```{r true-data, results = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
# create a single imputed, completely observed `boys` data set
set.seed(123)

>>>>

```{r true-data, include = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
# create a single imputed, completely observed `boys` data set
set.seed(123)

### 2021-11-03 manuscript/Submitted/Manuscript/Manuscript.Rmd

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"

# firstnote to eighthnote
firstnote: |
  These authors contributed equally to this work.
journal: psych
type: article
status: submit
bibliography: synth.bib
appendix: appendix.tex
abstract: |
  Synthetic data sets can greatly improve the dissemination of data 
  and further analysis of private data. Generating and analyzing synthetic data 
  sets is straightforward, yet a synthetic data analysis pipeline is 
  seldom adopted by applied researchers. We outline a simple procedure for 
  generating and analyzing synthetic data sets with `mice` in `R`. We demonstrate 
  using simulations that the analysis results obtained on synthetic data 
  yields unbiased and valid inferences, and leads to synthetic 
  records that cannot be distinguished from the true data records. The ease of use 
  when synthesizing data with `mice`, together with the validity of inferences 
  obtained through this procedure opens up a wealth of possibilities for data 
  dissemination and further research of initially private data. 
keywords: |
  mice; imputation; synthetic data.
authorcontributions: |
  The authors contributed equally to this work.
conflictsofinterest: |
  The authors declare no conflict of interest. 
sampleavailability: |
  A full simulation archive is available from the zip-enclosed RMD file
output: rticles::mdpi_article
---

>>>>

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
author:
  - name: Thom Volker
    affil: 1,*, \dagger
    orcid: 0000-0002-2408-7820
  - name: Gerko Vink
    affil: 1, \dagger
    orcid: 0000-0001-9767-1924
affiliation:
  - num: 1
    address: |
      Utrecht University - 
      Department of Methodology and Statistics. 
      Padualaan 14. 3584CH Utrecht, the Netherlands
# firstnote to eighthnote
firstnote: |
  These authors contributed equally to this work.
correspondence: |
  t.b.volker@uu.nl.
journal: psych
type: article
status: submit
bibliography: synth.bib
appendix: appendix.tex
abstract: |
  Synthetic data sets can greatly improve the dissemination of data 
  and further analysis of private data. Generating and analyzing synthetic data 
  sets is straightforward, yet a synthetic data analysis pipeline is 
  seldom adopted by applied researchers. We outline a simple procedure for 
  generating and analyzing synthetic data sets with `mice` in `R`. We demonstrate 
  using simulations that the analysis results obtained on synthetic data 
  yields unbiased and valid inferences, and leads to synthetic 
  records that cannot be distinguished from the true data records. The ease of use 
  when synthesizing data with `mice`, together with the validity of inferences 
  obtained through this procedure opens up a wealth of possibilities for data 
  dissemination and further research of initially private data. 
keywords: |
  mice; imputation; synthetic data.
acknowledgement: |
  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
  simulation study on an independent data set. 
authorcontributions: |
  The authors contributed equally to this work.
conflictsofinterest: |
  The authors declare no conflict of interest. 
sampleavailability: |
  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
output: rticles::mdpi_article
---
